---
title: "p8105_hw2_ac4140"
author: "Arielle"
date: "9/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (tidyverse)
```

##Question 1

#### First,read and cleaned the Mr. Trash Wheel Dataset

```{r}
health_harbor =
  readxl::read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
   sheet = "Mr. Trash Wheel") %>% 
  janitor::clean_names () %>% 
  select(-x15, -x16, -x17) %>% 
  drop_na(dumpster) %>%
  mutate(
    sports_balls = 
      as.integer (round(sports_balls, digit = 0))
  )
```

#### Reading in Precipitation 2017 Dataset

```{r}
prcp_2017 =
  readxl::read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
   sheet = "2017 Precipitation",
   range = "A2:B14") %>% 
  janitor::clean_names () %>% 
  drop_na(total)%>%
  mutate(
    year = 2017
  )
```

#### Reading in Precipitation 2018 Dataset

```{r}
prcp_2018 =
  readxl::read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx", 
   sheet = "2018 Precipitation",
   range = "A2:B14" ) %>% 
  janitor::clean_names () %>% 
  drop_na(total)%>%
  mutate(
    year = 2018
  )
```

#### Now I will combine the two Preciptation Data files into one

```{r}
prcp_full= 
  full_join(prcp_2017,prcp_2018) %>% 
  janitor:: clean_names() %>% 
  mutate(
    month = month.name[month]
  )
```

The number observations in the health_harbor dataset is `r nrow (health_harbor)`and the number of observations in prcp_2017 was `r nrow(prcp_2017)` and the number of observations in prcp_2018 was `r nrow(prcp_2018)`. The joined data set had `r nrow(prcp_full)` number of observations. Some key variables in the dataset included month total and years. The total precipitation in 2018 was `r sum(pull(prcp_2018, total))`The median number of sports balls in dumpster in 2017 was `r median (pull(health_harbor, sports_balls))`.

## Question 2 

### Reading in Fiver Thirty Eight Data Sets 
```{r}

```



